Develop atlantisom wrappers

### 2020-03-16 WrapperDevelopment.Rmd
still buggy
writing dat file now from proto-SS write wrapper

```{r ominit}

@@

library(here)
CC3om <- om_init(here("config/CC3config.r"))

@@

```{r inputs}

@@

```{r omindices}

@@

```{r omcomps}

@@

library(here)

@@

@@

if(fstepperyr>1){
  fish_len_comp_anndata <- fish_len_comp_data %>%
    mutate(yr = floor(time/fstepperyr)) %>%
    group_by(species, agecl, lower.bins, upper.bins, time=as.integer(yr)) %>%
    summarise(annnatlength=sum(atoutput)) %>%
    rename(atoutput = annnatlength)
} else {
  fish_len_comp_anndata <- fish_len_comp_data
}

@@

# need to fill empty length bins with 0s to have same bins as survey for SS_write_comps
missing.lengths <- setdiff(length_bins, names(fish_len_comp_final)[!names(fish_len_comp_final) %in% notbins])
fish_len_comp_final[as.character(missing.lengths)] <- 0                    # Add them, filled with '0's
fish_len_comp_final <- fish_len_comp_final[c("time", length_bins, "nsamp")]

# fishery age comps also 5 timesteps per year
if(fstepperyr>1){
  fish_age_comp_anndata <- fish_age_comp %>%
    mutate(yr = floor(time/fstepperyr)) %>%
    group_by(species, agecl, time=as.integer(yr)) %>%
    summarise(annnatage=sum(atoutput)) %>%
    rename(atoutput = annnatage)
} else {
  fish_age_comp_anndata <- fish_age_comp
}

>>>>

```{r ominit, eval=FALSE}

@@

library(here)
library(tidyverse)
library(atlantisom)
CC3om <- om_init(here("config/CC3config.r"))

@@

```{r inputs, eval=FALSE}

@@

```{r omindices, eval=FALSE}

@@

```{r omcomps, eval=FALSE}

@@

library(here)
library(tidyverse)
library(atlantisom)

@@

**See corrections below, in fishery time fixed and nsamp added to length comps**

@@

#add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))
fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

if(fstepperyr>1){
  fish_len_comp_anndata <- fish_len_comp_data %>%
    #mutate(yr = floor(time/fstepperyr)) %>%
    #group_by(species, agecl, lower.bins, upper.bins, time=as.integer(yr)) %>%
    group_by(species, agecl, lower.bins, upper.bins, time) %>% 
    summarise(annnatlength=sum(atoutput)) %>%
    rename(atoutput = annnatlength)
} else {
  fish_len_comp_anndata <- fish_len_comp_data
}

@@

# need to fill empty length bins with 0s to have same bins as survey for SS_write_comps
missing.lengths <- setdiff(length_bins, names(fish_len_comp_final)[!names(fish_len_comp_final) %in% notbins])
fish_len_comp_final[as.character(missing.lengths)] <- 0                    # Add them, filled with '0's
fish_len_comp_final <- fish_len_comp_final[c("time", length_bins, "nsamp")] #

# fishery age comps also 5 timesteps per year
if(fstepperyr>1){
  fish_age_comp_anndata <- fish_age_comp %>%
    #mutate(yr = floor(time/fstepperyr)) %>%
    #group_by(species, agecl, time=as.integer(yr)) %>%
    group_by(species, agecl, time) %>%
    summarise(annnatage=sum(atoutput)) %>%
    rename(atoutput = annnatage)
} else {
  fish_age_comp_anndata <- fish_age_comp
}
